---
title: "Development Metrics"
author: "Andrew Villeneuve"
date: "08/10/2020"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE,warning=F}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(rmarkdown)
library(dplyr)
library(ggplot2) 
library(forcats)
library(data.table)
library(AICcmodavg)
library(plyr)
library(MASS)
library(lme4)
library(AER)
library(car)
library(glmmTMB)
library(boot)
library(MuMIn)
library(PerformanceAnalytics)
library(scales)
library(glmmTMB)
library(betareg)
library(MASS)
library(gridExtra) 



#function used for creating prediction dataframe to then plot best fit lines
predictvals <- function(model, xvar, yvar, xrange=NULL, samples=100, ...) {

  # If xrange isn't passed in, determine xrange from the models.
  # Different ways of extracting the x range, depending on model type
  if (is.null(xrange)) {
    if (any(class(model) %in% c("lm", "glm")))
      xrange <- range(model$model[[xvar]])
    else if (any(class(model) %in% "loess"))
      xrange <- range(model$x)
  }
    newdata <- data.frame(x = seq(xrange[1], xrange[2], length.out = samples))
  names(newdata) <- xvar
  newdata[[yvar]] <- predict(model, newdata = newdata, ...)
  newdata
}

#overdispersion in glmms
overdisp_fun <- function(model) {
  
    rdf <- df.residual(model)
    rp <- residuals(model,type="pearson")
    Pearson.chisq <- sum(rp^2)
    prat <- Pearson.chisq/rdf
    pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}

data<-read.csv(here::here("data/hatch.dev.csv"))
str(data)
#we use hatchID to account for maternal effects - mother ID was not consistently gathered
hatchID<-read.csv(here::here("data/hatchID.csv"))

data$acc<-as.factor(data$acc)
colnames(data)[colnames(data)=="X..hatchlings"]<-"no.hatch"
data<-filter(data, acc != "NA")

##Photos of snail eggs were double checked for embryo counts across time. The maximum embryo count was recorded, and here we change the values as initially recorded to correct for undercounting. 
data<-filter(data, ocean != "NA")
which(data$site=="Wh")
data[92,1]<-"WH"
data[42,3]<-"P"
data[4,5]<-14
data[8,5]<-8
data[17,5]<-8
data[87,5]<-9
data[16,5]<-10
data[93,5]<-10
data[11,5]<-11
data[18,5]<-11
data[51,5]<-13
data[29,5]<-12
data[46,5]<-14
data[37,5]<-13
data[49,5]<-15
data[59,5]<-16
data[60,5]<-14
data[53,5]<-15
data[30,5]<-17
data[27,5]<-17
data[55,5]<-19
data[76,5]<-9
data[21,8]<-12
data<-data[-c(81),]

data$survivor <- (data$no.hatch / data$no.embryos)
data<-na.omit(data)
data$no.dead<-(data$no.embryos-data$no.hatch)
emb<-read.csv(here::here('data/embryos.l.csv'))
data<-merge(emb,data,by="eggID")
mom.size<-read.csv(here::here("data/momsize.csv"))
data.moms<-merge(mom.size,data,by="momID")
data<-merge(data,hatchID,by="eggID")

summary(data)

```

### The Study

Eggs laid by broodstock *Urosalpinx cinerea* from two Pacific sites and five Atlantic sites were collected and separated by population in individual tea strainers in two acclimation temperatures, 20° and 24°C. We reared these snails for use in the $CT_{max}$ experiment, but we were able to also gain valuable information on the embryo clutch/egg capsule, hatch time, and survival for each population. 

## Number of Embryos

After being laid and we had labeled individual egg cases in tea strainers, each egg case was photographed at least three times during development using a Leica digital microscope. From these photographs, we were able to establish the starting number of embryos in each capsule. The multiple photos allowed us to account embryos that may have been hidden in other photos. We did not count nurse embryos. 

## Hatching time

We checked adult broodstock every day for evidence of egg capsule laying. When capsules were identified, ideally with the mother still laying eggs, we removed each egg capsule, marked the mother, and noted the date of laying. Once the egg capsules were distributed into their separate tea strainers in respective acclimations, we checked daily for hatching. On the day of hatch, we marked the date. We counted an egg as hatched once the first juvenile crawled out of the top of the egg capsule, thus allowing for the free exchange of water inside the capsule and the ability for all juveniles to crawl out. 

## Survivorship

Once juveniles hatched from their capsules, we counted the number of juveniles that successfully developed into juvenile snails. To calcualte survivorship, we divided the number of initial embryos by the number of successfully developed juveniles 


## Metadata

# site
Two-letter abbreviation of sites used. Correspond to the following sites:

```{r}
site.meta<-data.table(siteID = c("GB","WH","OY","BF","FB","HM","TO"),site=c("Great Bay","Woods Hole","Oyster","Beaufort","Folly Beach","Humboldt","TO"),state=c("NH","MA","VA","NC","SC","CA","CA"))
site.meta
```
# lat

Latitude of the site 

# ocean

Used to sort out Atlantic and Pacific sites. A = Atlantic, P = Pacific

# acc

Acc is the acclimation temperature. Each population was reared in either 20°C or 24°C seawater (30PSU). We are interested in knowing if acclimation temperature will expose signs of plasticity in developmental rate and esurvivorhip for each population.

# no.embryos

The maxmum number of embryos counted in each egg capsule. This number sometimes was determined by advancing forward to later photos when embryos were obscured. "Nurse eggs" were not counted. 

# lay.date

Date egg capsules were first observed within broodstock tanks (m/dd/yyyy)

# date.hatched

Date at which the first snail was observed having emerged from the egg capsule OR date at which the egg capsule operculum was observed to be open, allowing seawater to enter the egg capsule freely. (m/dd/yyyy)

# no.hatch

Number of hatchling snails observed on date.hatched that were alive. Dead embryos were not counted.

# Time.to.hatch

Developmental time, calculated as the difference between lay.date and date.hatched. Measured in days

# survivor

Survivorship proportion for each egg capsule, calculated as no.hatch/no.embryos

# no.dead

Number of unsuccessful embryos per egg capsule, calculated as no.embryos - no.hatch

# mean

Mean SST for each site (degrees celsius)

# s.mean

Summer mean SST for each site, calculated as the range in values between 06/01 and 09/30. (degrees celsius)

# q.mean

Upper Quartile summer mean for each site, calculated as the upper 75th percentile of temperature observations over the summer (between 06/01 and 09/30). (degrees celsius)

# t.mean

Upper 90th percentile summer mean for each site, calculated over the summer (between 06/01 and 09/30). (degrees celsius)

# max

Maximum temperature for each site (degrees)

```{r, include=F,warning=F}

gbj<-read.csv(here::here('data/environmental_data/rawAtlantic/atl/gbj.csv'))
gbj$rdate<-as.POSIXct(gbj$DateTimeStamp,tz="","%m/%d/%Y%H:%M")
gbj$oce<-"a"
wh<-read.csv(here::here('data/environmental_data/rawAtlantic/atl/wh.csv'))
wh$rdate<-as.POSIXct(wh$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
wh$oce<-"a"
oy<-read.csv(here::here('data/environmental_data/rawAtlantic/atl/oy.csv'))
oy$rdate<-as.POSIXct(oy$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
oy$oce<-"a"
bf<-read.csv(here::here('data/environmental_data/rawAtlantic/atl/bf.csv'))
bf$rdate<-as.POSIXct(bf$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
bf$oce<-"a"
fb<-read.csv(here::here('data/environmental_data/rawAtlantic/atl/fb.csv'))
fb$rdate<-as.POSIXct(fb$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
fb$oce<-"a"
atll<-rbind(fb,bf,oy,wh,gbj)

to3<-read.csv(here::here('data/environmental_data/rawPacific/pac/to3.csv'))
to3$rdate<-as.POSIXct(to3$DateTimeStamp,tz="","%m/%d/%Y%H:%M")
to3$oce<-"p"
hmi2<-read.csv(here::here('data/environmental_data/rawPacific/pac/hmi2.csv'))
hmi2$rdate<-as.POSIXct(hmi2$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
hmi2$oce<-"p"

pac2<-rbind(to3,hmi2)
temp<-rbind(pac2,atll)
#mean annual temp
means<-data.frame(with(temp,tapply(WTMP,site,mean)))

#summer period
s.gbj<-filter(gbj,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.wh<-filter(wh,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.oy<-filter(oy,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.bf<-filter(bf,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.fb<-filter(fb,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.to3<-filter(to3,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.hmi2<-filter(hmi2,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")

##Quartiles
q<-data.frame("site" = c("gbj","wh","oy","bf","fb","hmi2","to3"),"quantile"=NA,"decile"=NA, "max"=NA)
q[1,2]<-quantile(s.gbj$WTMP,0.75,type=1)
q[2,2]<-quantile(s.wh$WTMP,0.75,type=1)
q[3,2]<-quantile(s.oy$WTMP,0.75,type=1)
q[4,2]<-quantile(s.bf$WTMP,0.75,type=1)
q[5,2]<-quantile(s.fb$WTMP,0.75,type=1)
q[6,2]<-quantile(s.hmi2$WTMP,0.75,type=1)
q[7,2]<-quantile(s.to3$WTMP,0.75,type=1)

q[1,3]<-quantile(s.gbj$WTMP,0.9,type=1)
q[2,3]<-quantile(s.wh$WTMP,0.9,type=1)
q[3,3]<-quantile(s.oy$WTMP,0.9,type=1)
q[4,3]<-quantile(s.bf$WTMP,0.9,type=1)
q[5,3]<-quantile(s.fb$WTMP,0.9,type=1)
q[6,3]<-quantile(s.hmi2$WTMP,0.9,type=1)
q[7,3]<-quantile(s.to3$WTMP,0.9,type=1)

q[1,4]<-s.gbj %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[2,4]<-s.wh %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[3,4]<-s.oy %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[4,4]<-s.bf %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[5,4]<-s.fb %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[6,4]<-s.hmi2 %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[7,4]<-s.to3 %>% group_by(WTMP) %>% summarise(Value = max(WTMP))


#MEAN SST
temp<-rbind(pac2,atll) #temperature data for all

means<-data.frame(with(temp,tapply(WTMP,site,mean)))

temp$means<-ifelse(temp$site=="bf",means[1,1], ifelse(temp$site=="oy",means[5,1],ifelse(temp$site=="wh",means[7,1],ifelse(temp$site=="gbj",means[3,1],ifelse(temp$site=="to3",means[6,1],ifelse(temp$site=="hmi2",means[4,1],ifelse(temp$site=="fb",means[2,1],NA))))))) #stitching temperature data to sites

temp$site_ID<-ifelse(temp$site=="bf","BF", ifelse(temp$site=="oy","OY",ifelse(temp$site=="wh","WH",ifelse(temp$site=="gbj","GB",ifelse(temp$site=="to3","TO",ifelse(temp$site=="hmi2","HM",ifelse(temp$site=="fb","FB",NA))))))) 


##SUMMER MEAN SST

summer.temp<-filter(temp,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.mean<-data.frame(with(summer.temp,tapply(WTMP,site,mean)))




data$mean<-ifelse(data$site=="BF",means[1,1], ifelse(data$site=="OY",means[5,1],ifelse(data$site=="WH",means[7,1],ifelse(data$site=="GB",means[3,1],ifelse(data$site=="TO",means[6,1],ifelse(data$site=="HM",means[4,1],ifelse(data$site=="FB",means[2,1],NA))))))) #stitching means sst data to sites

data$s.mean<-ifelse(data$site=="BF",s.mean[1,1], ifelse(data$site=="OY",s.mean[5,1],ifelse(data$site=="WH",s.mean[7,1],ifelse(data$site=="GB",s.mean[3,1],ifelse(data$site=="TO",s.mean[6,1],ifelse(data$site=="HM",s.mean[4,1],ifelse(data$site=="FB",s.mean[2,1],NA))))))) #stitching summer mean to stes

data$q.mean<-ifelse(data$site=="BF",q[4,2], ifelse(data$site=="OY",q[3,2],ifelse(data$site=="WH",q[2,2],ifelse(data$site=="GB",q[1,2],ifelse(data$site=="TO",q[7,2],ifelse(data$site=="HM",q[6,2],ifelse(data$site=="FB",q[5,2],NA))))))) #stitching summer mean to stes

data$t.mean<-ifelse(data$site=="BF",q[4,3], ifelse(data$site=="OY",q[3,3],ifelse(data$site=="WH",q[2,3],ifelse(data$site=="GB",q[1,3],ifelse(data$site=="TO",q[7,3],ifelse(data$site=="HM",q[6,3],ifelse(data$site=="FB",q[5,3],NA))))))) #stitching summer mean to stes

data$max<-ifelse(data$site=="BF",q[4,4], ifelse(data$site=="OY",q[3,4],ifelse(data$site=="WH",q[2,4],ifelse(data$site=="GB",q[1,4],ifelse(data$site=="TO",q[7,4],ifelse(data$site=="HM",q[6,4],ifelse(data$site=="FB",q[5,4],NA)))))))

#season length
#egg laying mean
lay_fb<-mean((filter(fb,rdate>"2018-03-01 00:00:00" & rdate< "2018-03-30 00:00:00"))$WTMP)
lay_bf<-mean((filter(bf,rdate>"2018-03-15 00:00:00" & rdate< "2018-04-15 00:00:00"))$WTMP)
lay_oy<-mean((filter(oy,rdate>"2018-05-01 00:00:00" & rdate< "2018-05-30 00:00:00"))$WTMP)
lay_wh<-mean((filter(wh,rdate>"2018-05-15 00:00:00" & rdate< "2018-06-15 00:00:00"))$WTMP)
lay_gb<-mean((filter(gbj,rdate>"2018-06-01 00:00:00" & rdate< "2018-06-30 00:00:00"))$WTMP)
lay_hm<-mean((filter(hmi2,rdate>"2018-04-15 00:00:00" & rdate< "2018-05-15 00:00:00"))$WTMP)#inat
lay_to<-mean((filter(to3,rdate>"2018-04-15 00:00:00" & rdate< "2018-05-15 00:00:00"))$WTMP)#ruesink
#max
lay_fb2<-mean((filter(fb,rdate>"2018-03-01 00:00:00" & rdate< "2018-05-30 00:00:00"))$WTMP)
lay_bf2<-mean((filter(bf,rdate>"2018-03-15 00:00:00" & rdate< "2018-05-30 00:00:00"))$WTMP)
lay_oy2<-mean((filter(oy,rdate>"2018-05-01 00:00:00" & rdate< "2018-07-30 00:00:00"))$WTMP)
lay_wh2<-mean((filter(wh,rdate>"2018-07-01 00:00:00" & rdate< "2018-08-31 00:00:00"))$WTMP)
lay_gb2<-mean((filter(gbj,rdate>"2018-07-01 00:00:00" & rdate< "2018-08-31 00:00:00"))$WTMP)
lay_hm2<-mean((filter(hmi2,rdate>"2018-06-1 00:00:00" & rdate< "2018-07-15 00:00:00"))$WTMP)#inat
lay_to2<-mean((filter(to3,rdate>"2018-06-1 00:00:00" & rdate< "2018-07-15 00:00:00"))$WTMP)#ruesink

data$lay1<-ifelse(data$site=="BF",lay_bf,ifelse(data$site=="FB",lay_fb,ifelse(data$site=="GB",lay_gb,ifelse(data$site=="HM",lay_hm,ifelse(data$site=="OY",lay_oy,ifelse(data$site=="TO",lay_to,ifelse(data$site=="WH",lay_wh,NA)))))))

data$lay2<-ifelse(data$site=="BF",lay_bf2,ifelse(data$site=="FB",lay_fb2,ifelse(data$site=="GB",lay_gb2,ifelse(data$site=="HM",lay_hm2,ifelse(data$site=="OY",lay_oy2,ifelse(data$site=="TO",lay_to2,ifelse(data$site=="WH",lay_wh2,NA)))))))

##counts by site and acclimation 
counts<-ddply(data,.(data$site,data$acc),nrow)
names(counts)<-c("Site","Acclimation","N")
a<-aggregate(data$no.embryos,by=list(data$site,data$acc),FUN=mean)
names(a)<-c("Site","Acclimation","mean")
counts<-cbind(counts,a$mean)
counts
names(counts)<-c("Site","Acclimation","N","Mean")
```

## Testing for collinearity

It appears that survival and Time to hatching are correlated, and so should not be included together in models.
```{r,echo=F,warning=F}
data[,c(2,3,8,12)]->a
a<-na.omit(a)
c<-cor(a)
chart.Correlation(c)
```

Does mom weight or mom length correlate with number of embryos? They do not appear to, but We will include moms in mixed effect models

```{r,echo=F,warning=F}


ggplot(data.moms,aes(x=no.embryos,y=mom.wt))+geom_point()
a<-lm(no.embryos~mom.wt,data.moms)
summary(a)

ggplot(data.moms,aes(x=site,y=mom.l))+geom_point()
```

## Number of Embryos analysis

```{r,echo=F,warning=F}

data$no.embryos<-as.integer(data$no.embryos)
data$momID<-as.factor(data$momID)
data$hatchID<-as.factor(data$hatchID)


#scaling and centering our variables

 data2<-data.frame("lat"=scale(data$lat,center=T,scale=T),"mean"=scale(data$mean,center=T,scale=T),"s.mean"=scale(data$s.mean,center=T,
    scale=T),"t.mean"=scale(data$t.mean,center=T,scale=T),"q.mean"=scale(data$q.mean,center=T,scale=T),no.embryos=data$no.embryos,momID=
    data$momID,acc=data$acc)
    data2$site<-data$site

  ##THESE WORK, but slow! 
  a<-glmmTMB(no.embryos ~ 1+(1|hatchID), data=data,family=compois)
  b<-glmmTMB(no.embryos ~ lat+(1|hatchID),data=data,family=compois)
  c<-glmmTMB(no.embryos ~ mean+(1|hatchID),data=data,family=compois)
  d<-glmmTMB(no.embryos ~ s.mean+(1|hatchID),data=data,family=compois)
  e<-glmmTMB(no.embryos ~ q.mean+(1|hatchID),data=data,family=compois)
  f<-glmmTMB(no.embryos ~ t.mean+(1|hatchID),data=data,family=compois)
  g<-glmmTMB(no.embryos ~ max+(1|hatchID),data=data,family=compois)
  h<-glmmTMB(no.embryos ~ lay1+(1|hatchID),data=data,family=compois)
  i<-glmmTMB(no.embryos ~ lay2+(1|hatchID),data=data,family=compois)
 
  
  
  noe<-list(a,b,c,d,e,f,g,h,i)
  aictab(noe)
  
  #global model
  model<-glm(no.embryos ~q.mean+t.mean+s.mean+mean+lat,data=data,family="poisson")

1/(car::vif(model))

#four models are well supported, so we will model average
  modeavelist<-list(g,f,e,d)
  summary(model.avg(modeavelist))
  
  ##troubleshooting
  
  cts<-dplyr::count(data2,momID)
  ggplot(data2,aes(x=momID,y=no.embryos))+facet_wrap(momID~.)+geom_point()
  
#for purpose of plotting, let's use the model with best support
noem<-glmmTMB(no.embryos ~ max+(1|momID),data=data,family=compois)
summary(noem)


E1<-resid(f,type="pearson")
N<-nrow(data)
p<-length(coef(f))
sum(E1^2) / (N-p)

overdisp_fun(noem)

#no overdispersion!


#acquire r^2
sjstats::r2(d)
```
So, the null model predicts this the best. We can say that the number of embryos does not appear to really change by home population. But, a few models were within the 2 delta AIC limit. So let's plot with one. 

```{r,echo=F,warning=F}


fig9a<-ggplot(data,aes(x=max,y=no.embryos))+theme_classic()+ylab("Number of Embryos/Egg Capsule")+theme(text=element_text(family="arial",size=18))+labs(y="Clutch Size",x=expression(atop(paste("T"[hab]," (SST °C)"))))+geom_jitter(width=0.2,height=0.2,size=3)+ geom_smooth(method="lm",color="black",se=F)+scale_x_continuous(breaks=c(22,26,30,34))


fig9a


```

## Time to hatch analysis
```{r,warning=F,echo=F}


tth<-list(
  "null"=glmmTMB(Time.to.hatch ~ 1+(1|momID),data,family="gaussian"),
  "lat"=glmmTMB(Time.to.hatch ~ lat+(1|momID),data,family="gaussian"),
  "mean"=glmmTMB(Time.to.hatch ~ mean+(1|momID),data,family="gaussian"),
  "s.mean"=glmmTMB(Time.to.hatch ~ s.mean+(1|momID),data,family="gaussian"),
  "q.mean"=glmmTMB(Time.to.hatch ~ q.mean+(1|momID),data,family="gaussian"),
  "t.mean"=glmmTMB(Time.to.hatch ~ t.mean+(1|momID),data,family="gaussian"),
  "lat+acc"=glmmTMB(Time.to.hatch ~ lat+acc+(1|momID),data,family="gaussian"),
  "mean+acc"=glmmTMB(Time.to.hatch ~ mean+acc+(1|momID),data,family="gaussian"),
  "s.mean+acc"=glmmTMB(Time.to.hatch ~ s.mean+acc+(1|momID),data,family="gaussian"),
  "q.mean+acc"=glmmTMB(Time.to.hatch ~ q.mean+acc+(1|momID),data,family="gaussian"),
  "t.mean+acc"=glmmTMB(Time.to.hatch ~ t.mean+acc+(1|momID),data,family="gaussian"),
  "lat*acc"=glmmTMB(Time.to.hatch ~ lat*acc+(1|momID),data,family="gaussian"),
  "mean*acc"=glmmTMB(Time.to.hatch ~ mean*acc+(1|momID),data,family="gaussian"),
  "s.mean*acc"=glmmTMB(Time.to.hatch ~ s.mean*acc+(1|momID),data,family="gaussian"),
  "q.mean*acc"=glmmTMB(Time.to.hatch ~ q.mean*acc+(1|momID),data,family="gaussian"),
  "t.mean*acc"=glmmTMB(Time.to.hatch ~ t.mean*acc+(1|momID),data,family="gaussian"),
  "max*acc"=glmmTMB(Time.to.hatch ~ max*acc+(1|momID),data,family="gaussian"),
  "max+acc"=glmmTMB(Time.to.hatch ~ max+acc+(1|momID),data,family="gaussian"),
  "max"=glmmTMB(Time.to.hatch ~ max+(1|momID),data,family="gaussian"),
  
  "clutch_null"=glmmTMB(Time.to.hatch ~ 1+(1|hatchID),data,family="gaussian"),
  "clutch_lat"=glmmTMB(Time.to.hatch ~ lat+(1|hatchID),data,family="gaussian"),
  "clutch_mean"=glmmTMB(Time.to.hatch ~ mean+(1|hatchID),data,family="gaussian"),
  "clutch_s.mean"=glmmTMB(Time.to.hatch ~ s.mean+(1|hatchID),data,family="gaussian"),
  "clutch_q.mean"=glmmTMB(Time.to.hatch ~ q.mean+(1|hatchID),data,family="gaussian"),
  "clutch_t.mean"=glmmTMB(Time.to.hatch ~ t.mean+(1|hatchID),data,family="gaussian"),
  "clutch_lat+acc"=glmmTMB(Time.to.hatch ~ lat+acc+(1|hatchID),data,family="gaussian"),
  "clutch_mean+acc"=glmmTMB(Time.to.hatch ~ mean+acc+(1|hatchID),data,family="gaussian"),
  "clutch_s.mean+acc"=glmmTMB(Time.to.hatch ~ s.mean+acc+(1|hatchID),data,family="gaussian"),
  "clutch_q.mean+acc"=glmmTMB(Time.to.hatch ~ q.mean+acc+(1|hatchID),data,family="gaussian"),
  "clutch_t.mean+acc"=glmmTMB(Time.to.hatch ~ t.mean+acc+(1|hatchID),data,family="gaussian"),
  "clutch_lat*acc"=glmmTMB(Time.to.hatch ~ lat*acc+(1|hatchID),data,family="gaussian"),
  "clutch_mean*acc"=glmmTMB(Time.to.hatch ~ mean*acc+(1|hatchID),data,family="gaussian"),
  "clutch_s.mean*acc"=glmmTMB(Time.to.hatch ~ s.mean*acc+(1|hatchID),data,family="gaussian"),
  "clutch_q.mean*acc"=glmmTMB(Time.to.hatch ~ q.mean*acc+(1|hatchID),data,family="gaussian"),
  "clutch_t.mean*acc"=glmmTMB(Time.to.hatch ~ t.mean*acc+(1|hatchID),data,family="gaussian"),
  "clutch_max*acc"=glmmTMB(Time.to.hatch ~ max*acc+(1|hatchID),data,family="gaussian"),
  "clutch_max+acc"=glmmTMB(Time.to.hatch ~ max+acc+(1|hatchID),data,family="gaussian"),
  "clutch_max"=glmmTMB(Time.to.hatch ~ max+(1|hatchID),data,family="gaussian"))

aictab(tth)

#two models are top. Let's model average

model<-glm(Time.to.hatch ~q.mean+t.mean+s.mean+mean+lat+no.embryos+survivor,data=data,family="gaussian")

1/(car::vif(model))

#two models are under AIC 2, so we will model average them for reporting. For plotting, we will use the best supported model. 
a<-glmmTMB(Time.to.hatch ~ lat*acc+(1|momID),data,family="gaussian")
b<-glmmTMB(Time.to.hatch ~ mean*acc+(1|momID),data,family="gaussian")
summary(model.avg(a,b))

tthm<-tth$'clutch_mean*acc'
summary(tthm)

#how do the residuals look
hist(resid(tthm))

r.squaredGLMM(tthm)

data %>%
  group_by(site,acc)%>%
  summarise_at(vars("Time.to.hatch"),mean)


data %>%
  group_by(site,acc)%>%
  summarise_at(vars("Time.to.hatch"),sd)


#silenced post hoc comparisons
#TukeyHSD((aov(Time.to.hatch~site*acc,data=data)))
```

Now that we have a model averaged summary of our data, we will plot one of the best fit models (mean temperature) for visualization. 

```{r,warning=F,echo=F}
make_model_tth<-function(data) {glm(Time.to.hatch ~ mean,data,family="gaussian")}
models_tth<-dlply(data,"acc",.fun=make_model_tth)

predvals.tth<-ldply(models_tth,.fun=predictvals,xvar="mean",yvar="Time.to.hatch")
#geom_line(data=predvals.tth)

ggplot(data,aes(x=mean,y=Time.to.hatch,color=acc,fill=acc,shape=ocean))+scale_color_manual(labels=c("20°C","24°C"),name="Acclimation",values=c("blue","red"))+theme_classic()+scale_shape_manual(labels=c("Atlantic","Pacific"),name="Ocean",values=c(21,24))+theme(text=element_text(family="arial",size=22))+scale_fill_manual(labels=c("20°C","24°C"),name="Acclimation",values=c("blue","red"))+geom_jitter(width=.05,size=2)+
  geom_segment(aes(x = 12.10044, xend = 20.34944, y = (46.0815-15.2972 )   + (-0.4575+ 0.2777 )  *12.10044	, yend = (46.0815-15.2972 )   + (-0.4575+ 0.2777 )   *20.34944	),size=1.5,color='red')+
  geom_segment(aes(x = 12.10044, xend = 20.34944, y = (46.0815 )   + (-0.4575)  *12.10044	, yend = (46.0815 )   + (-0.4575)   *20.34944	),size=1.5,color='blue')+
  labs(y="Time to hatch (d)", x=expression(paste("T"[hab], " (SST °C)")))


```

## Survivorship analysis

```{r,warning=F,echo=F}

hist(data$survivor)


y=cbind(data$no.hatch,data$no.dead)
y<-na.omit(y)
surv<-list(
  "clutch_null"=glmmTMB(y ~ (1|hatchID), data,family=binomial),
  "clutch_lat"=glmmTMB(y ~ lat+(1|hatchID),data,family=binomial),
  "clutch_mean"=glmmTMB(y ~ mean+(1|hatchID),data,family=binomial),
  "clutch_s.mean"=glmmTMB(y ~ s.mean+(1|hatchID),data,family=binomial),
  "clutch_q.mean"=glmmTMB(y ~ q.mean+(1|hatchID),data,family=binomial),
  "clutch_t.mean"=glmmTMB(y ~ t.mean+(1|hatchID),data,family=binomial),
  "clutch_lat+acc"=glmmTMB(y ~ lat+acc+(1|hatchID),data,family=binomial),
  "clutch_mean+acc"=glmmTMB(y ~ mean+acc+(1|hatchID),data,family=binomial),
  "clutch_s.mean+acc"=glmmTMB(y ~ s.mean+acc+(1|hatchID),data,family=binomial),
  "clutch_q.mean+acc"=glmmTMB(y ~ q.mean+acc+(1|hatchID),data,family=binomial),
  "clutch_t.mean+acc"=glmmTMB(y ~ t.mean+acc+(1|hatchID),data,family=binomial),
  "clutch_lat*acc"=glmmTMB(y ~ lat*acc+(1|hatchID),data,family=binomial),
  "clutch_mean*acc"=glmmTMB(y ~ mean*acc+(1|hatchID),data,family=binomial),
  "clutch_s.mean*acc"=glmmTMB(y ~ s.mean*acc+(1|hatchID),data,family=binomial),
  "clutch_q.mean*acc"=glmmTMB(y ~ q.mean*acc+(1|hatchID),data,family=binomial),
  "clutch_t.mean*acc"=glmmTMB(y ~ t.mean*acc+(1|hatchID),data,family=binomial),
  "clutch_max*acc"=glmmTMB(y ~ max*acc+(1|hatchID),data,family=binomial),
  "clutch_max+acc"=glmmTMB(y ~ max+acc+(1|hatchID),data,family=binomial),
  "clutch_max"=glmmTMB(y ~ max+(1|hatchID),data,family=binomial))


aictab(surv)
subset<-subset(aictab(surv),Delta_AICc<2)#choosing which models
subset

a<-glmmTMB(y ~ q.mean+(1|hatchID),data,family=binomial)
b<-glmmTMB(y ~ s.mean+(1|hatchID),data,family=binomial)
c<-glmmTMB(y ~ t.mean+(1|hatchID),data,family=binomial)
d<-glmmTMB(y ~ q.mean+acc+(1|hatchID),data,family=binomial)
e<-glmmTMB(y ~ s.mean+acc+(1|hatchID),data,family=binomial)
g<-glmmTMB(y ~ t.mean+acc+(1|hatchID),data,family=binomial)
h<-glmmTMB(y ~ lat+(1|hatchID),data,family=binomial)
i<-glmmTMB(y ~ max+(1|hatchID),data,family=binomial)


#a bunch of top models. Time to model average
surv.ave<-model.avg(a,b,c,d,e,g,h,i)
summary(surv.ave)

#one model performs best, so we will use this one for visualziation (upper 25th percentile)
summary(glmmTMB(y ~ q.mean+(1|momID),data=data,family=binomial()))


survm<-glmmTMB(survivor ~ q.mean+(1|momID),data=data,family=binomial)
E1<-resid(survm,type="pearson")
N<-nrow(data)
p<-length(coef(survm))
sum(E1^2) / (N-p)

overdisp_fun(survm)

#not overdispersed

model<-glm(y ~q.mean+t.mean+s.mean+mean+lat+no.embryos+survivor+Time.to.hatch,data=data,family="binomial")

#not multicollinear
1/(car::vif(model))

r.squaredGLMM(a)

```

The summer mean only is the best predictor of survivorship. I decided to ignore number of embryos and time to hatch for now. 

```{r,warning=F,echo=F}
#model for plotting
data3<-na.omit(data2)


y2=cbind(data3$no.hatch,data3$no.dead)
y2<-na.omit(y2)
model2<-glm(y ~ q.mean,data3,family=binomial)
xmin<-min(data3$q.mean,na.rm=T)
xmax<-max(data3$q.mean,na.rm=T)
pred.surv<-data.frame(q.mean=seq(xmin,xmax,length.out=100))
pred.surv$survivor<-predict(model2,pred.surv)

c0<-(-0.99210)
c1<-0.07876
```
```{r,warning=F,echo=F}
q.mean<-data$q.mean
p1=plogis(c0+c1*q.mean)
comb<-data.frame(q.mean,p1)
data$survivor<-data$survivor

fig9b<-ggplot(data,aes(x=q.mean,y=survivor))+stat_smooth(data=comb,aes(x=q.mean,y=p1),method="glm", family=binomial, formula=y~x,color="black")+theme_classic()+theme(text=element_text(family="arial",size=18))+labs(y="Clutch Survivorship",x=expression(atop(paste("T"[hab]," (SST °C)"))))+geom_jitter(width=0.1,height=0.1,size=3)

fig9b

gridExtra::grid.arrange(fig9a,fig9b,ncol=2)

```

```{r,include=F,warning=F}
#printing results of time to hatch
 sink("tthm.txt")
 print(summary(glmmTMB(Time.to.hatch ~ mean*acc*no.embryos+(1|momID),data,family="gaussian")))
 sink()
```