---
title: "QSG 11/18"
author: "Andrew Villeneuve"
date: "11/13/2019"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(rmarkdown)
library(dplyr)
library(ggplot2) 
library(forcats)
library(data.table)
library(AICcmodavg)
library(plyr)
library(MASS)
library(lme4)
library(AER)
library(car)
library(glmmTMB)
library(boot)
 
predictvals <- function(model, xvar, yvar, xrange=NULL, samples=100, ...) {

  # If xrange isn't passed in, determine xrange from the models.
  # Different ways of extracting the x range, depending on model type
  if (is.null(xrange)) {
    if (any(class(model) %in% c("lm", "glm")))
      xrange <- range(model$model[[xvar]])
    else if (any(class(model) %in% "loess"))
      xrange <- range(model$x)
  }
    newdata <- data.frame(x = seq(xrange[1], xrange[2], length.out = samples))
  names(newdata) <- xvar
  newdata[[yvar]] <- predict(model, newdata = newdata, ...)
  newdata
}

#overdispersion in glmms
overdisp_fun <- function(model) {
  
    rdf <- df.residual(model)
    rp <- residuals(model,type="pearson")
    Pearson.chisq <- sum(rp^2)
    prat <- Pearson.chisq/rdf
    pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}

setwd("C:/Users/drewv/Documents/UMASS/data")
data<-read.csv("hatch.dev.csv")
str(data)

data$acc<-as.factor(data$acc)
colnames(data)[colnames(data)=="X..hatchlings"]<-"no.hatch"
data<-filter(data, acc != "NA")

##Photos of snail eggs were double checked for embryo counts across time. The maximum embryo count was recorded, and here we change the values as initially recorded to correct for undercounting. 
data<-filter(data, ocean != "NA")
which(data$site=="Wh")
data[92,1]<-"WH"
data[42,3]<-"P"
data[4,5]<-14
data[8,5]<-8
data[17,5]<-8
data[87,5]<-9
data[16,5]<-10
data[93,5]<-10
data[11,5]<-11
data[18,5]<-11
data[51,5]<-13
data[29,5]<-12
data[46,5]<-14
data[37,5]<-13
data[49,5]<-15
data[59,5]<-16
data[60,5]<-14
data[53,5]<-15
data[30,5]<-17
data[27,5]<-17
data[55,5]<-19
data[76,5]<-9
data[21,8]<-12
data<-data[-c(81),]

data$survivor <- (data$no.hatch / data$no.embryos)
data<-na.omit(data)
data$no.dead<-(data$no.embryos-data$no.hatch)
emb<-read.csv('embryos.l.csv')
data<-merge(emb,data,by="eggID")
mom.size<-read.csv("momsize.csv")
data.moms<-merge(mom.size,data,by="momID")

summary(data)

```

### The Study

Eggs laid by broodstock *Urosalpinx cinerea* from two Pacific sites and five Atlantic sites were collected and separated by population in individual tea strainers in two acclimation temperatures, 20° and 24°C. We reared these snails for use in the $CT_{max}$ experiment, but we were able to also gain valuable information on the embryo clutch/egg capsule, hatch time, and survival for each population. 

## Metadata

# site
Two-letter abbreviation of sites used. Correspond to the following sites:

```{r}
site.meta<-data.table(siteID = c("GB","WH","OY","BF","FB","HM","TO"),site=c("Great Bay","Woods Hole","Oyster","Beaufort","Folly Beach","Humboldt","TO"),state=c("NH","MA","VA","NC","SC","CA","CA"))
site.meta
```
# lat

Latitude of the site 

# ocean

Used to sort out Atlantic and Pacific sites. A = Atlantic, P = Pacific

# acc

Acc is the acclimation temperature. Each population was reared in either 20°C or 24°C seawater (30PSU). We are interested in knowing if acclimation temperature will expose signs of plasticity in developmental rate and esurvivorhip for each population.

# no.embryos

The maxmum number of embryos counted in each egg capsule. This number sometimes was determined by advancing forward to later photos when embryos were obscured. "Nurse eggs" were not counted. 

# lay.date

Date egg capsules were first observed within broodstock tanks

# date.hatched

Date at which the first snail was observed having emerged from the egg capsule OR date at which the egg capsule operculum was observed to be open, allowing seawater to enter the egg capsule freely. 

# no.hatch

Number of hatchling snails observed on date.hatched that were alive. Dead embryos were not counted.

# Time.to.hatch

Developmental time, calculated as the difference between lay.date and date.hatched

# survivor

Survivorship proportion for each egg capsule, calculated as no.hatch/no.embryos

# no.dead

Number of unsuccessful embryos per egg capsule, calculated as no.embryos - no.hatch

# mean

Mean SST for each site

# s.mean

Summer mean SST for each site, calculated as the range in values between 06/01 and 09/30.

# q.mean

Upper Quartile summer mean for each site, calcualted as the upper 75th percentile of temperature observations over the summer (between 06/01 and 09/30)

# t.mean

Upper 90th percentile summer mean for each site, calculated over the summer (between 06/01 and 09/30)

```{r, include=F}
setwd('C:/Users/drewv/Documents/UMASS/SSTdata/rawAtlantic/atl')
library(scales)

gbj<-read.csv('gbj.csv',header=T)
gbj$rdate<-as.POSIXct(gbj$DateTimeStamp,tz="","%m/%d/%Y%H:%M")
wh<-read.csv('wh.csv',header=T)
wh$rdate<-as.POSIXct(wh$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
oy<-read.csv('oy.csv',header=T)
oy$rdate<-as.POSIXct(oy$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
bf<-read.csv('bf.csv',header=T)
bf$rdate<-as.POSIXct(bf$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
fb<-read.csv('fb.csv',header=T)
fb$rdate<-as.POSIXct(fb$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
dm<-read.csv('dm.csv',header=TRUE)
dm$rdate<-as.POSIXct(dm$DateTimeStamp,tz="","%m/%d/%Y")
gcsk<-read.csv('gcsk.csv',header=TRUE)
gcsk$rdate<-as.POSIXct(gcsk$DateTimeStamp,tz="","%m/%d/%Y%H:%M")
atll<-rbind(gcsk,gbj,bf,oy,wh,fb)
setwd('C:/Users/drewv/Documents/UMASS/SSTdata/rawPacific/pac')
nah1516<-read.csv('nahcotta_2015_2016.csv',header=T)#2015 through August, 2016 data after that
nah1516$rdate<-as.POSIXct(nah1516$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")
hmi2<-read.csv('hmi2.csv',header=T)
hmi2$rdate<-as.POSIXct(hmi2$DateTimeStamp,tz="", "%m/%d/%Y%H:%M")#Indian island 2015
to3<-read.csv('to3.csv',header=TRUE)
to3$rdate<-as.POSIXct(to3$DateTimeStamp,tz="","%m/%d/%Y%H:%M")##stitched 2014 and 2015 (post Nove. 21 data together)

pac2<-rbind(nah1516,to3,hmi2)
temp<-rbind(pac2,atll)
means<-data.frame(with(temp,tapply(WTMP,site,mean)))

s.gbj<-filter(gbj,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.wh<-filter(wh,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.oy<-filter(oy,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.bf<-filter(bf,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.fb<-filter(fb,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.gcsk<-filter(gcsk,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.to3<-filter(to3,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.hmi2<-filter(hmi2,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.nah1516<-filter(nah1516,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")

##Quartiles
q<-data.frame("site" = c("gbj","wh","oy","bf","fb","gcsk","nah1516","hmi2","to3"),"quantile"=NA,"decile"=NA)
q[1,2]<-quantile(s.gbj$WTMP,0.75,type=1)
q[2,2]<-quantile(s.wh$WTMP,0.75,type=1)
q[3,2]<-quantile(s.oy$WTMP,0.75,type=1)
q[4,2]<-quantile(s.bf$WTMP,0.75,type=1)
q[5,2]<-quantile(s.fb$WTMP,0.75,type=1)
q[6,2]<-quantile(s.gcsk$WTMP,0.75,type=1)
q[7,2]<-quantile(s.nah1516$WTMP,0.75,type=1)
q[8,2]<-quantile(s.hmi2$WTMP,0.75,type=1)
q[9,2]<-quantile(s.to3$WTMP,0.75,type=1)

q[1,3]<-quantile(s.gbj$WTMP,0.9,type=1)
q[2,3]<-quantile(s.wh$WTMP,0.9,type=1)
q[3,3]<-quantile(s.oy$WTMP,0.9,type=1)
q[4,3]<-quantile(s.bf$WTMP,0.9,type=1)
q[5,3]<-quantile(s.fb$WTMP,0.9,type=1)
q[6,3]<-quantile(s.gcsk$WTMP,0.9,type=1)
q[7,3]<-quantile(s.nah1516$WTMP,0.9,type=1)
q[8,3]<-quantile(s.hmi2$WTMP,0.9,type=1)
q[9,3]<-quantile(s.to3$WTMP,0.9,type=1)

q[1,4]<-s.gbj %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[2,4]<-s.wh %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[3,4]<-s.oy %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[4,4]<-s.bf %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[5,4]<-s.fb %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[6,4]<-s.gcsk %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[7,4]<-s.nah1516 %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[8,4]<-s.hmi2 %>% group_by(WTMP) %>% summarise(Value = max(WTMP))
q[9,4]<-s.to3 %>% group_by(WTMP) %>% summarise(Value = max(WTMP))


##SUMMER MEAN SST

summer.temp<-filter(temp,rdate>"2018-06-01 00:00:00" & rdate< "2018-09-30 00:00:00")
s.mean<-data.frame(with(summer.temp,tapply(WTMP,site,mean)))




data$mean<-ifelse(data$site=="BF",means[6,1], ifelse(data$site=="OY",means[7,1],ifelse(data$site=="WH",means[8,1],ifelse(data$site=="GB",means[5,1],ifelse(data$site=="TO",means[2,1],ifelse(data$site=="HM",means[3,1],ifelse(data$site=="WP",means[1,1],ifelse(data$site=="SK",means[4,1],ifelse(data$site=="FB",means[9,1],NA))))))))) #stitching means sst data to sites

data$s.mean<-ifelse(data$site=="BF",s.mean[6,1], ifelse(data$site=="OY",s.mean[7,1],ifelse(data$site=="WH",s.mean[8,1],ifelse(data$site=="GB",s.mean[5,1],ifelse(data$site=="TO",s.mean[2,1],ifelse(data$site=="HM",s.mean[3,1],ifelse(data$site=="WP",s.mean[1,1],ifelse(data$site=="SK",s.mean[4,1],ifelse(data$site=="FB",s.mean[9,1],NA))))))))) #stitching summer mean to stes

data$q.mean<-ifelse(data$site=="BF",q[4,2], ifelse(data$site=="OY",q[3,2],ifelse(data$site=="WH",q[2,2],ifelse(data$site=="GB",q[1,2],ifelse(data$site=="TO",q[9,2],ifelse(data$site=="HM",q[8,2],ifelse(data$site=="WP",q[7,2],ifelse(data$site=="SK",q[6,2],ifelse(data$site=="FB",q[5,2],NA))))))))) #stitching summer mean to stes

data$t.mean<-ifelse(data$site=="BF",q[4,3], ifelse(data$site=="OY",q[3,3],ifelse(data$site=="WH",q[2,3],ifelse(data$site=="GB",q[1,3],ifelse(data$site=="TO",q[9,3],ifelse(data$site=="HM",q[8,3],ifelse(data$site=="WP",q[7,3],ifelse(data$site=="SK",q[6,3],ifelse(data$site=="FB",q[5,3],NA))))))))) #stitching summer mean to stes

data$max<-ifelse(data$site=="BF",q[4,4], ifelse(data$site=="OY",q[3,4],ifelse(data$site=="WH",q[2,4],ifelse(data$site=="GB",q[1,4],ifelse(data$site=="TO",q[9,4],ifelse(data$site=="HM",q[8,4],ifelse(data$site=="WP",q[7,4],ifelse(data$site=="SK",q[6,4],ifelse(data$site=="FB",q[5,4],NA)))))))))

##counts by site and acclimation 
counts<-ddply(data,.(data$site,data$acc),nrow)
names(counts)<-c("Site","Acclimation","N")
a<-aggregate(data$no.embryos,by=list(data$site,data$acc),FUN=mean)
names(a)<-c("Site","Acclimation","mean")
counts<-cbind(counts,a$mean)
counts
names(counts)<-c("Site","Acclimation","N","Mean")
```

## Testing for collinearity

It appears that survival and Time to hatching are correlated, and so should not be included in models.
```{r}
library(PerformanceAnalytics)
data[,c(3,8,12,14)]->a
a<-na.omit(a)
c<-cor(a)
chart.Correlation(c)

ggplot(data.moms,aes(x=no.embryos,y=mom.wt))+geom_point()
a<-lm(no.embryos~mom.wt,data.moms)
summary(a)

ggplot(data.moms,aes(x=site,y=mom.l))+geom_point()
```

## Number of Embryos

```{r}

data$no.embryos<-as.integer(data$no.embryos)
data$momID<-as.factor(data$momID)

 data2<-data.frame("lat"=scale(data$lat,center=T,scale=T),"mean"=scale(data$mean,center=T,scale=T),"s.mean"=scale(data$s.mean,center=T,
    scale=T),"t.mean"=scale(data$t.mean,center=T,scale=T),"q.mean"=scale(data$q.mean,center=T,scale=T),no.embryos=data$no.embryos,momID=
    data$momID,acc=data$acc)
    data2$site<-data$site
# 
# noe<-list(
#   "null"=glm(no.embryos ~ 1, data=data,family=poisson),
#   "lat"=glm(no.embryos ~ lat,data=data,family=poisson),
#   "mean"=glm(no.embryos ~ mean,data=data,family=poisson),
#   "s.mean"=glm(no.embryos ~ s.mean,data=data,family=poisson),
#   "q.mean"=glm(no.embryos ~ q.mean,data=data,family=poisson),
#   "t.mean"=glm(no.embryos ~ t.mean,data=data,family=poisson))
#   noe2<-list(
#   "null.m"<-glmmTMB(no.embryos ~ 1+(1|site/momID), data=data2,family=nbinom2),
#   "lat.m"=glmmTMB(no.embryos ~ lat+(1|site/momID),data=data2,family=nbinom2),
#   "mean.m"=glmmTMB(no.embryos ~ mean+(1|site/momID),data=data2,family=nbinom2),
#   "s.mean.m"=glmmTMB(no.embryos ~ s.mean+(1|site/momID),data=data2,family=nbinom2),
#   "q.mean.m"=glmmTMB(no.embryos ~ q.mean+(1|site/momID),data=data2,family=nbinom2),
#   "t.mean.m"=glmmTMB(no.embryos ~ t.mean+(1|site/momID),data=data2,family=nbinom2))
#   
#  
#   
#   a<-glmmTMB(no.embryos ~ (1|site/momID), data=data2,family=nbinom2)
#   b<-glmmTMB(no.embryos ~ lat+(1|site/momID),data=data2,family=nbinom2)
#   c<-glmmTMB(no.embryos ~ mean+(1|site/momID),data=data2,family=nbinom2)
#   d<-glmmTMB(no.embryos ~ s.mean+(1|site/momID),data=data2,family=nbinom2)
#   e<-glmmTMB(no.embryos ~ q.mean+(1|site/momID),data=data2,family=nbinom2)
#   f<-glmmTMB(no.embryos ~ t.mean+(1|site/momID),data=data2,family=nbinom2)
#   
#   #new models with brian
#   
# 
#   
#   b2<-glmmTMB(no.embryos ~ lat+(1|momID),data=data2,family=nbinom1,ziformula=~0)
#   b3<-glmmTMB(no.embryos ~ lat+(1|momID),data=data2,family=poisson)
#   b2.a<-glmmTMB(no.embryos ~ lat+(1|momID),data=data2,family=nbinom1,ziformula=~0)
#   b4<-glmmTMB(no.embryos ~ lat+(1|site/momID),data=data2,family=nbinom1,ziformula=~0)
  
  ##THESE WORK
  a<-glmmTMB(no.embryos ~ 1+(1|site/momID), data=data,family=compois)
  b<-glmmTMB(no.embryos ~ lat+(1|site/momID),data=data,family=compois)
  c<-glmmTMB(no.embryos ~ mean+(1|site/momID),data=data,family=compois)
  d<-glmmTMB(no.embryos ~ s.mean+(1|site/momID),data=data,family=compois)
  e<-glmmTMB(no.embryos ~ q.mean+(1|site/momID),data=data,family=compois)
  f<-glmmTMB(no.embryos ~ t.mean+(1|site/momID),data=data,family=compois)
  g<-glmmTMB(no.embryos ~ lat+ocean+(1|site/momID),data=data,family=compois)
  h<-glmmTMB(no.embryos ~ mean+ocean+(1|site/momID),data=data,family=compois)
  i<-glmmTMB(no.embryos ~ s.mean+ocean+(1|site/momID),data=data,family=compois)
  j<-glmmTMB(no.embryos ~ q.mean+ocean+(1|site/momID),data=data,family=compois)
  k<-glmmTMB(no.embryos ~ t.mean+ocean+(1|site/momID),data=data,family=compois)
  l<-glmmTMB(no.embryos ~ max+(1|site/momID),data=data,family=compois)
  m<-glmmTMB(no.embryos ~ max+ocean+(1|site/momID),data=data,family=compois)
  
  noe<-list(a,b,c,d,e,f,g,h,i,j,k,l,m)
  
  model<-glm(no.embryos ~q.mean+t.mean+s.mean+mean+lat,data=data,family="poisson")

1/(car::vif(model))

  modeavelist<-list(a,d,e,f,l,m)
  summary(model.avg(modeavelist))
  
  ##troubleshooting
  
  cts<-dplyr::count(data2,momID)
  ggplot(data2,aes(x=momID,y=no.embryos))+facet_wrap(momID~.)+geom_point()
  
aictab(noe)
noem<-glmmTMB(no.embryos ~ t.mean+(1|site/momID),data=data,family=compois)
summary(noem)


E1<-resid(f,type="pearson")
N<-nrow(data)
p<-length(coef(f))
sum(E1^2) / (N-p)

overdisp_fun(noem)

#no overdispersion!


r.squaredGLMM(f)


```
So, the null model predicts this the best. We can say that the number of embryos does not appear to really change by home population. But, a few models were within the 2 delta AIC limit. So let's plot with one. 

```{r}
model1<-glmmTMB(no.embryos ~ t.mean,data=data,family=compois)
xmin<-min(data$t.mean,na.rm=T)
xmax<-max(data$t.mean,na.rm=T)
pred.noe<-data.frame(t.mean=seq(xmin,xmax,length.out=100))
pred.noe$no.embryos<-predict(model1,pred.noe)
pred.noe$no.embryos<-exp(pred.noe$no.embryos)



fig9a<-ggplot(data,aes(x=t.mean,y=no.embryos))+theme_classic()+ylab("Number of Embryos/Egg Capsule")+xlab("Mean SST °C (90th percentile summer months)")+theme(text=element_text(family="arial",size=18))+labs(y="Clutch Size",x=expression(atop(paste("T"[hab]),"(SST °C; 90th percentile summer months)")))+geom_jitter(width=0.2,height=0.2,size=3)

fig9a


```

## Time to hatch
```{r}


tth<-list(
  "null"=glmmTMB(Time.to.hatch ~ 1+(1|momID),data,family="gaussian"),
  "lat"=glmmTMB(Time.to.hatch ~ lat+(1|momID),data,family="gaussian"),
  "mean"=glmmTMB(Time.to.hatch ~ mean+(1|momID),data,family="gaussian"),
  "s.mean"=glmmTMB(Time.to.hatch ~ s.mean+(1|momID),data,family="gaussian"),
  "q.mean"=glmmTMB(Time.to.hatch ~ q.mean+(1|momID),data,family="gaussian"),
  "t.mean"=glmmTMB(Time.to.hatch ~ t.mean+(1|momID),data,family="gaussian"),
  "lat+acc"=glmmTMB(Time.to.hatch ~ lat+acc+(1|momID),data,family="gaussian"),
  "mean+acc"=glmmTMB(Time.to.hatch ~ mean+acc+(1|momID),data,family="gaussian"),
  "s.mean+acc"=glmmTMB(Time.to.hatch ~ s.mean+acc+(1|momID),data,family="gaussian"),
  "q.mean+acc"=glmmTMB(Time.to.hatch ~ q.mean+acc+(1|momID),data,family="gaussian"),
  "t.mean+acc"=glmmTMB(Time.to.hatch ~ t.mean+acc+(1|momID),data,family="gaussian"),
  "lat*acc"=glmmTMB(Time.to.hatch ~ lat*acc+(1|momID),data,family="gaussian"),
  "mean*acc"=glmmTMB(Time.to.hatch ~ mean*acc+(1|momID),data,family="gaussian"),
  "s.mean*acc"=glmmTMB(Time.to.hatch ~ s.mean*acc+(1|momID),data,family="gaussian"),
  "q.mean*acc"=glmmTMB(Time.to.hatch ~ q.mean*acc+(1|momID),data,family="gaussian"),
  "t.mean*acc"=glmmTMB(Time.to.hatch ~ t.mean*acc+(1|momID),data,family="gaussian"),
  "max*acc"=glmmTMB(Time.to.hatch ~ max*acc+(1|momID),data,family="gaussian"),
  "max+acc"=glmmTMB(Time.to.hatch ~ max+acc+(1|momID),data,family="gaussian"),
    "max"=glmmTMB(Time.to.hatch ~ max+(1|momID),data,family="gaussian"))

  #   "lat+acc+e"=glmmTMB(Time.to.hatch ~ lat+acc+no.embryos+(1|momID),data,family="gaussian"),
  # "mean+acc+e"=glmmTMB(Time.to.hatch ~ mean+acc+no.embryos+(1|momID),data,family="gaussian"),
  # "s.mean+acc+e"=glmmTMB(Time.to.hatch ~ s.mean+acc+no.embryos+(1|momID),data,family="gaussian"),
  # "q.mean+acc+e"=glmmTMB(Time.to.hatch ~ q.mean+acc+no.embryos+(1|momID),data,family="gaussian"),
  # "t.mean+acc+e"=glmmTMB(Time.to.hatch ~ t.mean+acc+no.embryos+(1|momID),data,family="gaussian"),
  # "lat*acc*e"=glmmTMB(Time.to.hatch ~ lat*acc*no.embryos+(1|momID),data,family="gaussian"),
  # "mean*acc*e"=glmmTMB(Time.to.hatch ~ mean*acc*no.embryos+(1|momID),data,family="gaussian"),
  # "s.mean*acc*e"=glmmTMB(Time.to.hatch ~ s.mean*acc*no.embryos+(1|momID),data,family="gaussian"),
  # "q.mean*acc*e"=glmmTMB(Time.to.hatch ~ q.mean*acc*no.embryos+(1|momID),data,family="gaussian"),
  # "t.mean*acc*e"=glmmTMB(Time.to.hatch ~ t.mean*acc*no.embryos+(1|momID),data,family="gaussian")


aictab(tth)

#two models are top. Let's model average

model<-glm(Time.to.hatch ~q.mean+t.mean+s.mean+mean+lat+no.embryos+survivor,data=data,family="gaussian")

1/(car::vif(model))

a<-glmmTMB(Time.to.hatch ~ lat*acc+(1|momID),data,family="gaussian")
b<-glmmTMB(Time.to.hatch ~ mean*acc+(1|momID),data,family="gaussian")
summary(model.avg(a,b))

tthm<-tth$'mean*acc'
summary(tthm)
0.9671/(0.9671+2.2702)

hist(resid(tthm))

r.squaredGLMM(tthm)

data %>%
  group_by(site,acc)%>%
  summarise_at(vars("Time.to.hatch"),mean)


data %>%
  group_by(site,acc)%>%
  summarise_at(vars("Time.to.hatch"),sd)

TukeyHSD((aov(Time.to.hatch~site*acc,data=data)))
```
Not sure what to do here. Is this multivariate? For now, let's just ignore the number of embryos as a predictor for hatching time and model. Time to hatch increases significantly with decreasing mean SST and decreases with a higher acclimation.

```{r}
make_model_tth<-function(data) {glm(Time.to.hatch ~ mean,data,family="gaussian")}
models_tth<-dlply(data,"acc",.fun=make_model_tth)

predvals.tth<-ldply(models_tth,.fun=predictvals,xvar="mean",yvar="Time.to.hatch")
#geom_line(data=predvals.tth)

ggplot(data,aes(x=mean,y=Time.to.hatch,color=acc,fill=acc,shape=ocean))+scale_color_manual(labels=c("20°C","24°C"),name="Acclimation",values=c("blue","red"))+theme_classic()+scale_shape_manual(labels=c("Atlantic","Pacific"),name="Ocean",values=c(21,24))+theme(text=element_text(family="arial",size=22))+scale_fill_manual(labels=c("20°C","24°C"),name="Acclimation",values=c("blue","red"))+geom_jitter(width=.05,size=2)+
  geom_segment(aes(x = 12.10044, xend = 20.34944, y = (46.0815-15.2972 )   + (-0.4575+ 0.2777 )  *12.10044	, yend = (46.0815-15.2972 )   + (-0.4575+ 0.2777 )   *20.34944	),size=1.5,color='red')+
  geom_segment(aes(x = 12.10044, xend = 20.34944, y = (46.0815 )   + (-0.4575)  *12.10044	, yend = (46.0815 )   + (-0.4575)   *20.34944	),size=1.5,color='blue')+
  labs(y="Time to hatch (d)", x=expression(paste("T"[hab], " (SST °C)")))


```

## Survivorship

```{r}
library('glmmTMB')
library('betareg')
library(MASS)
hist(data$survivor)
y.transf.betareg <- function(y){
    n.obs <- sum(!is.na(y))
    (y * (n.obs - 1) + 0.5) / n.obs
}
y=cbind(data$no.hatch,data$no.dead)
y<-na.omit(y)
surv<-list(
  "null"=glmmTMB(y ~ (1|momID), data,family=binomial),
  "lat"=glmmTMB(y ~ lat+(1|momID),data,family=binomial),
  "mean"=glmmTMB(y ~ mean+(1|momID),data,family=binomial),
  "s.mean"=glmmTMB(y ~ s.mean+(1|momID),data,family=binomial),
  "q.mean"=glmmTMB(y ~ q.mean+(1|momID),data,family=binomial),
  "t.mean"=glmmTMB(y ~ t.mean+(1|momID),data,family=binomial),
  "lat+acc"=glmmTMB(y ~ lat+acc+(1|momID),data,family=binomial),
  "mean+acc"=glmmTMB(y ~ mean+acc+(1|momID),data,family=binomial),
  "s.mean+acc"=glmmTMB(y ~ s.mean+acc+(1|momID),data,family=binomial),
  "q.mean+acc"=glmmTMB(y ~ q.mean+acc+(1|momID),data,family=binomial),
  "t.mean+acc"=glmmTMB(y ~ t.mean+acc+(1|momID),data,family=binomial),
  "lat*acc"=glmmTMB(y ~ lat*acc+(1|momID),data,family=binomial),
  "mean*acc"=glmmTMB(y ~ mean*acc+(1|momID),data,family=binomial),
  "s.mean*acc"=glmmTMB(y ~ s.mean*acc+(1|momID),data,family=binomial),
  "q.mean*acc"=glmmTMB(y ~ q.mean*acc+(1|momID),data,family=binomial),
  "t.mean*acc"=glmmTMB(y ~ t.mean*acc+(1|momID),data,family=binomial),
  "max*acc"=glmmTMB(y ~ max*acc+(1|momID),data,family=binomial),
  "max+acc"=glmmTMB(y ~ max+acc+(1|momID),data,family=binomial),
  "max"=glmmTMB(y ~ max+(1|momID),data,family=binomial))

  
 # "lat+acc+e"=glm(y ~ lat+acc+no.embryos,data,family="binomial"),
  #"mean+acc+e"=glm(y ~ mean+acc+no.embryos,data,family="binomial"),
#  "s.mean+acc+e"=glm(y ~ s.mean+acc+no.embryos,data,family="binomial"),
 # "q.mean+acc+e"=glm(y ~ q.mean+acc+no.embryos,data,family="binomial"),
  #"t.mean+acc+e"=glm(y ~ t.mean+acc+no.embryos,data,family="binomial"),
#  "lat*acc*e"=glm(y ~ lat*acc*no.embryos,data,family="binomial"),
 # "mean*acc*e"=glm(y ~ mean*acc*no.embryos,data,family="binomial"),
#  "s.mean*acc*e"=glm(y ~ s.mean*acc*no.embryos,data,family="binomial"),
 # "q.mean*acc*e"=glm(y ~ q.mean*acc*no.embryos,data,family="binomial"),
#  "t.mean*acc*e"=glm(y ~ t.mean*acc*no.embryos,data,family="binomial"),
 # "lat+e"=glm(y ~ lat+no.embryos,data,family="binomial"),
#  "mean+e"=glm(y ~ mean+no.embryos,data,family="binomial"),
#  "s.mean+e"=glm(y ~ s.mean+no.embryos,data,family="binomial"),
#  "q.mean+e"=glm(y ~ q.mean+no.embryos,data,family="binomial"),
#  "t.mean+e"=glm(y ~ t.mean+no.embryos,data,family="binomial"),
#  "lat*e"=glm(y ~ lat*no.embryos,data,family="binomial"),
#  "mean*e"=glm(y ~ mean*no.embryos,data,family="binomial"),
#  "s.mean*e"=glm(y ~ s.mean*no.embryos,data,family="binomial"),
#  "q.mean*e"=glm(y ~ q.mean*no.embryos,data,family="binomial"),
#  "t.mean*e"=glm(y ~ t.mean*no.embryos,data,family="binomial"),

aictab(surv)
library(MuMIn)
subset<-subset(aictab(surv),Delta_AICc<2)#choosing which models

a<-glmmTMB(y ~ q.mean+(1|momID),data,family=binomial)
b<-glmmTMB(y ~ s.mean+(1|momID),data,family=binomial)
c<-glmmTMB(y ~ t.mean+(1|momID),data,family=binomial)
d<-glmmTMB(y ~ q.mean+acc+(1|momID),data,family=binomial)
e<-glmmTMB(y ~ s.mean+acc+(1|momID),data,family=binomial)
g<-glmmTMB(y ~ t.mean+acc+(1|momID),data,family=binomial)
h<-glmmTMB(y ~ lat+(1|momID),data,family=binomial)
i<-glmmTMB(y ~ max+(1|momID),data,family=binomial)


surv.ave<-model.avg(a,b,c,d,e,g,h,i)
summary(surv.ave)

summary(glmmTMB(y ~ q.mean+(1|momID),data=data,family=binomial()))

.3794/(.3794+0.6159 )

survm<-glmmTMB(survivor ~ q.mean+(1|momID),data=data,family=binomial)
E1<-resid(survm,type="pearson")
N<-nrow(data)
p<-length(coef(survm))
sum(E1^2) / (N-p)

overdisp_fun(survm)

#not overdispersed

model<-glm(y ~q.mean+t.mean+s.mean+mean+lat+no.embryos+survivor+Time.to.hatch,data=data,family="binomial")

#not multicollinear
1/(car::vif(model))

r.squaredGLMM(i)

```

The summer mean only is the best predictor of survivorship. I decided to ignore number of embryos and time to hatch for now. 

```{r}
#model for plotting
data3<-na.omit(data2)


y2=cbind(data3$no.hatch,data3$no.dead)
y2<-na.omit(y2)
model2<-glm(y ~ q.mean,data3,family=binomial)
xmin<-min(data3$q.mean,na.rm=T)
xmax<-max(data3$q.mean,na.rm=T)
pred.surv<-data.frame(q.mean=seq(xmin,xmax,length.out=100))
pred.surv$survivor<-predict(model2,pred.surv)

#c0=coef(model2)[1] #model intercept 
#c1=coef(model2)[2] #model slope 

c0=-0.43225
c1=0.0828

q.mean<-data$q.mean
p1=plogis(c0+c1*q.mean)
comb<-data.frame(q.mean,p1)
data$survivor<-data$survivor

fig9b<-ggplot(data,aes(x=q.mean,y=survivor))+stat_smooth(data=comb,aes(x=q.mean,y=p1),method="glm", family=binomial, formula=y~x,color="black")+theme_classic()+theme(text=element_text(family="arial",size=18))+labs(y="Clutch Survivorship",x=expression(atop(paste("T"[hab]),"(SST °C; 75th percentile summer months)")))+geom_jitter(width=0.1,height=0.1,size=3)

fig9b

grid.arrange(fig9a,fig9b,ncol=2)

```

```{r,include=F}
#printing results of time to hatch
 sink("tthm.txt")
 print(summary(glmmTMB(Time.to.hatch ~ mean*acc*no.embryos+(1|momID),data,family="gaussian")))
 sink()
```